Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-10-28 cvpr2018.tex
modify methods
fix methdos

\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU \cite{} (the depth depends on the input image size) until the feature map has $512{\times}4{\times}4$ dimension. There two branches are added on top of it for multi-purpose discriminator design (see next section) . One is a direct $4{\times}4$ conv layers to produce a 2-d vector to classify real and fake. Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding). Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results. Finally, a $4{\times}4$ conv layer produces a 2-d vector.

\textbf{Advantages} Figure \ref{fig:archs-compare} illustrates the architecture difference between widely-used cascade strategy \cite{han2017stackgan,denton2015deep} and our strategy. Compared with it, 
\\

@@

\textbf{Notation } 
We denote the training data set by $S=\{(\bm{X}^n, \bm{T}^n),n=1,...,N\}$, where $X^n$ is the $n-$th training image, and $T^n={t^1,...,t^m}$ as $m$ text descriptions corresponds to $X^n$. Our goal is to learn the generator $G$ that is capable of producing high resolution images of high visual quality as well as variability giving an input text description $t$.

@@

\textbf{Variational text embedding } Following the practice of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $\psi_t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$. This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}. In addition, using this kind of text embedding makes the input pure stochastic, making it more difficult for the generator to over fit the training data.

 In the spirit of variational auto-encoder, further Kullback-Leibler divergence regularization term  $D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I}))$ is added to the final loss function to push the Gaussian distribution to the norm distribution to address over-fitting.  In addition, this term might also play a role in balancing the $c_t$ and generated condition vector $c_t$ by forcing $c$ to have a similar scale to $z$.  In the following sections, we denote $c_t$ as the variational conditional text vector.

@@

Our architecture of $G$ consists of a single stream network with additional multiple side outputs. This architecture resemble the previous proposed method in edge detection\cite{hed} and classification\cite{deepsup}, which demonstrate that additional supervision to the hidden layer can improve both generalization and optimization.  We hypothesis that adding hidden layer supervision using side outputs can act as a regularizer to the hidden space of $G$, which reduces the over-fitting issue and provide a short path for the error signal.

Given a random Gaussian noise  $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$ and a text description $t$, to obtain the text embedding vector $\psi_{t}\in \mathcal{R}^{T}$, we apply a per-trained text encoder on the image description $t$, in this paper, we use the char-rnn based text encoder provided in \cite{reed2016generative}.  $G$ will generate multiple side outputs,
\begin{equation}
\label{side}
\begin{split}
	o_1,...,o_s = G(\psi_{t}, z)	   
\end{split}
\end{equation}
where $s$ is the total number of side outputs, please note that the dimension of $o_1,..,o_s$ increase gradually (e.g., 64$\times$64, 128$\times$128, and 256$\times$256). Denote $\mathcal{X}^i = \{X^i_1, .. X^i_s\}$ as the pyramid of  resized images constructed from original image $X^i$.

@@

\begin{equation}
\label{equ:optim}
\begin{split}
  G^*, \mathcal{D}^* = \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(G,\mathcal{D}, \mathcal{X}, \bm{T} , z)
\end{split}
\end{equation}
where $\mathcal{D}^*$ compresses the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} , z)$ is the full objective of this mini-max game.

@@

\begin{equation}
\label{equ:matchignloss}
\begin{split}
\mathcal{L}_{pair}(D_i)  = & \mathbb{E}_{(x, t) \sim p_{data}}[(D_i( {X_i},  \bm{t}) - 1) ^ 2 ] - \frac{1}{2}*\\ 
&   \mathbb{E}_{(X_i, \hat{t}) \sim p_{data}}[(D_i({X_i}, \hat{\bm{t}}) - 1)^2  ] - \frac{1}{2} *\\
&   \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, \bm{t}))^2 ]  
\end{split}
\end{equation}

Similarly, the pair wise objective of generator can be summarized as:
\begin{equation}
\label{equ:pariG}
\begin{split}
\mathcal{L}_{pair}(G)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, \bm{t}) - 1) )^2 ] )
\end{split}
\end{equation}

@@

The pair-loss is designed to differentiated invalid pairs from valid ones. However, at the very beginning of the training, the generated images are far away from true image distribution, the discriminator can very easily to judge a pair as valid without using much pair information. \textcolor{red}{need more explanationn.}

Our insight has two folds:
1. Image loss without using pair sentence information can be beneficial in the sense that it utilize more information as well as it directly push the generated image to the true image distribution. We hypothesis this type of loss can help the model to stabilize and boost the training. 
2. Since our model outputs a pyramid of side outputs with increasing image size. We expect the low resolution output can capture the global structure and color information, while the higher resolution outputs paints more details and focus on rendering the image.

We don't only want the whole image is classified as true image by the discriminator, but also restrict the discriminator to classify all the local patches of high resolution output as true as well.   To this end, we propose a hierarchical image loss, where the output of the image  discriminator is more than one scale value.
\begin{equation}
  d_i = D_i(X_i)
\end{equation}
The size of $d_i$ increases as $X_i$. For instance 1$\times$1 for 64$\times$64 input, 4$\times 4$ for 128$\times$128, etc. This type of design, gradually increase the receptive field of the discriminator.

This loss explicit force the discriminator to differentiate correct pair from the wrong pair.  However, there is no explicit loss that push the discriminator to differentiate real images from the fake images. The way that they formulate all the task into pair based solution complicate the task of the generator. In this paper, we propose to directly add another loss that concentrate the image quality only beside the matching loss. Specifically, it can be given by:
\begin{equation}
\label{equ:local}
\begin{split}
\mathcal{L}_{local}(K_i)  = & \mathbb{E}_{(x, t) \sim p_{data}}[(K_i( {X_i}) - 1) ^ 2 ] -  \mathbb{E}_{t \sim p_{data}}[ (K_i( {o}_i))^2 ]  
\end{split}
\end{equation}

Similarly, the pair wise objective of generator can be summarized as:
\begin{equation}
\label{equ:pariG}
\begin{split}
\mathcal{L}_{local}(G)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (K_i( {o}_i) - 1) )^2 ] )
\end{split}
\end{equation}

\textcolor{red}{equations needs to be verified, just a rough place holder}

Further more, this separation of the image loss from the matching loss open further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator. \textcolor{red}{maybe utilizing the imagenet for training the coco, or save as another paper.}

\subsection{Total Loss}
The total objective for both $D$ and $G$ can be given by. 
\begin{equation}
\label{equ:totalD}
\begin{split}
\mathcal{L}(D)  = & \sum_{i=1}^{s} ( \mathcal{L}_{pair}(D) + \alpha~\mathcal{L}_{local}(D) ) 
\end{split}
\end{equation}

\begin{equation}
\label{equ:totalG}
\begin{split}
\mathcal{L}(G)  = & \sum_{i=1}^{s} ( \mathcal{L}_{pair}(G) + \alpha~\mathcal{L}_{local}(G) + \\
                  & \beta~D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) )  
\end{split}
\end{equation}
where $\alpha$ is coefficient used to tune the weight of the local patch loss, $\beta$ is used to tune the weights of the KL-Divergence.  A algorithm that summarizes the training process of our model is given in Algorithm 1.

%The loss function of the matching aware discriminator are summarized as:
%\begin{equation}
%\label{matchignloss}
%\begin{split}
%\mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
%&\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
%&   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
%\end{split}
%\end{equation}
%
%\begin{equation}
%\label{matchignloss}
%\begin{split}
%\mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
%&\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
%&   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
%\end{split}
%\end{equation}

\subsection{Implementation Details}
\begin{equation}
 \label{genloss}
 \begin{split}
 \mathcal{L}_G = & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{sent}( G(z, c_t),  \psi_t) ) ] + \\
				  & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
                  & D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
 \end{split}
 \end{equation}
 where $c_t$ is the variational conditional vector generated from $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$. To make the network differentiable, in practice, we adopted the re-parametric trick\cite{vae}, where $c_t$ is actually computed as $\mu(\psi_t)+\Sigma(\psi_t)\odot \epsilon$, where $\epsilon\in \mathcal{R}^{T}$ is draw from a normal Gaussian distribution.

 \begin{algorithm}
 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.\textcolor{red}{need to change to goodfellow algorithm style}}
 	\label{CHalgorithm}
 	\begin{algorithmic}[1]

 		\For{$i \gets 1 \textrm{ to } S$ }
 		\State $z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
 		\State $\hat{x_1}, \hat{x_2} = G(z_1, \psi_t),  G(z_2, \psi_{\hat{t}})$ %\{Forward through $G$ using matching text embedding\}
 		\State $d_r$ = $D_{pair}(x, \psi_t)$ \{(real image, matching text)\}
 		\State $d_w$ = $D_{pair}(x, \psi_{\hat{t}})$ \{(real image, wrong text)\}
 		\State $d_f$ = $D_{pair}(\hat{x_1}, \psi_t)$ \{(fake image, matching text)\}
 		\State $s_r, s_1, s_2$ = $D_{img}(x), D_{img}(\hat{x_1})$, $D_{img}(\hat{x_1})$ %\{Forward through $D_{img}$ with $\hat{x_1}$\}

 		\State $loss_{img}$ = $ (\log(1-s_1) + \log(1-s_2))/2 $
 		\State $loss_{pair}$ = $ (\log(1-d_w) + \log(1-d_f))/2 $

 		\State $\mathcal{L}_{D}$ = $\log(d_r) + \log(s_r) +loss_{img} + loss_{pair}$
 		\State $\mathcal{L}_{G}$ = $\log(1-d_f) +  ( \log(1-s_1) + \log(1-s_2) )/2 $
 		\State $\theta_G$ = $\theta_G$ - ${\delta \mathcal{L}_G } / {\delta \theta_G}$  \{Update generator\}
 		\State $\theta_D$ = $\theta_D$ - ${\delta \mathcal{L}_D} / {\delta \theta_D}$  \{Update generator\}

@@

@@

\subsection{Implementation Details}

>>>>

@@

\textbf{Notation } 
We denote the training data set by $S=\{(\bm{X}^n, \bm{T}^n),n=1,...,N\}$, where $X^n$ is the $n-$th training image, and $T^n={t^1,...,t^m}$ as $m$ text descriptions corresponds to $X^n$.

Since we obtain the text embedding vector  using the per-trained char-rnn text encoder provided in \cite{reed2016generative}. For simplicity, we don not differentiate text description and the corresponding embedding vector in this paper.  Our goal is to learn the generator $G$ that is capable of producing high resolution images of high visual quality as well as variability giving an input text description $t$.

@@

\textbf{Variational text embedding } Following the practice of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(t), \Sigma(t) )$, in which the mean $\mu(t)$ and the diagonal covariance matrix $\Sigma(t)$ are non-linear transformation of the original text embedding $t$. This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}. In addition, using this kind of text embedding makes the input pure stochastic, making it more difficult for the generator to over fit the training data.

@@

Our architecture of $G$ consists of a single stream network with additional multiple side outputs. This architecture resemble the previous proposed method in edge detection\cite{xie2015holistically} and classification\cite{lee2015deeply}, which demonstrate that additional supervision to the hidden layer can improve both generalization and optimization.  We hypothesis that adding hidden layer supervision using side outputs can act as a regularizer to the hidden space of $G$, which reduces the over-fitting issue and provide a short path for the error signal.

Given a random Gaussian noise  $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$ and a text description embedding $t$  $G$ will generate multiple side outputs,
\begin{equation}
\label{side}
\begin{split}
	o_1,...,o_s = G(t, z)	   
\end{split}
\end{equation}
where $s$ is the total number of side outputs, please note that the dimension of $o_1,..,o_s$ increase gradually (e.g., 64$\times$64, 128$\times$128, and 256$\times$256). Denote $\mathcal{X}^i = \{X^i_1, .. X^i_s\}$ as the pyramid of  resized images constructed from original image $X^i$.  For simplicity, we represent $o=\{o_1,...,o_s\}$.

@@

\begin{equation}
\label{equ:optim}
\begin{split}
  G^*, \mathcal{D}^* = \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(G,\mathcal{D}, \mathcal{X}, \bm{T})
\end{split}
\end{equation}
where $\mathcal{D}^*$ compresses the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.

@@

\begin{equation}
\label{equ:matchignloss}
\begin{split}
\mathcal{L}_{pair}(D_i)  = & \mathbb{E}_{(x, t) \sim p_{data}}[(D_i( {X_i},  {t}) - 1) ^ 2 ] - \frac{1}{2}*\\ 
&   \mathbb{E}_{(X_i, \hat{t}) \sim p_{data}}[(D_i({X_i}, \hat{{t}}) - 1)^2  ] - \frac{1}{2} *\\
&   \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, {t}))^2 ]  
\end{split}
\end{equation}

Similarly, the pair wise objective of generator can be summarized as:
\begin{equation}
\label{equ:pariG}
\begin{split}
\mathcal{L}_{pair}(G)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, {t}) - 1) )^2 ] )
\end{split}
\end{equation}

@@

The pair-loss is designed to differentiate invalid pairs from valid ones.
It works by first translating the image to a compact size code, then the combination of the image code and the sentence vector is concatenated and fed to successive layers of non-linear transformation  to predict the validity of the image sentence pair.

Overall, the pair loss is designed to capture the global context semantic information.  However, this loss has two problems, firstly,  there is no explicit loss that push the discriminator to differentiate real images from the fake images. Combining both tasks (generating realistic images and matching image with text) into one outputs complicates the learning tasks. Second,  as the image resolution goes higher, it might be challenging for the global pair wise discriminator to capture the local fine-grained details.  In addition, as is pointed in \cite{shrivastava2016learning}, a single global strong discriminator tend to over-emphasize certain image feature and may lead to artifacts.

%More specifically, ideally the image patches sampled from the higher resolution outputs

Our solutions is to add hierarchical local adversarial image loss which does not require sentence information, to all the side outputs. To make the image discriminator focus more on local details, we restrict the receptive field of the image discriminator.
Our insight has two folds:
\begin{itemize}
	\item 1. Forcing the local patch of generated samples to have similar statistics to real image patch can be beneficial to rendering details. %

	\item 2. Image loss without using pair sentence information can be beneficial in the sense that it utilize more information as well as it directly push the generated image to the true image distribution. We hypothesis this type of loss can help the model to stabilize and boost the training. 
\end{itemize}
%In addition, at the very beginning of the training,  generated images are usually far away from true image distribution, the discriminator can very easily judge a pair as invalid without using much pair information. \textcolor{red}{need more explanationn.}
%We not only want the whole image is classified as true image by the discriminator, but also want to restrict the discriminator to classify all the local patches of high resolution output as true as well.   
Since our model outputs a pyramid of outputs with increasing image sizes. 
We expect the low resolution output capture the global structure and color information, while the higher resolution outputs focus on rendering the image details.

To force the discriminator focus on the fine-grained details, a nature way is to fix the receptive field for all the generator. To this end, we propose a hierarchical image loss, where the output of image  discriminator is a grid of values.

Denote $K_i$ as the $i-$th local image discriminators,  the output $d_i = K_i(X_i)$ has a size increasing with input $X_i$. For instance 1$\times$1 for 64$\times$64 input, 4$\times 4$ for 128$\times$128 and 8$\times 8$ for 256$\times$256 etc.  In this way, even the resolutions goes higher, the receptive field keeps unchanged.

Specifically, the proposed local image loss can be given by:
\begin{equation}
\label{equ:local}
\begin{split}
\mathcal{L}_{local}(K_i, X_i, o_i, t )  = & \mathbb{E}_{(x, t) \sim p_{data}}[(K_i( {X_i}) - 1) ^ 2 ] - \\
&  \mathbb{E}_{t \sim p_{data}}[ (K_i( {o}_i))^2 ]  
\end{split}
\end{equation}

Similarly, the pair wise objective of generator can be summarized as:
\begin{equation}
\label{equ:pariG}
\begin{split}
\mathcal{L}_{local}(G, o)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (K_i( {o}_i) - 1) )^2 ] )
\end{split}
\end{equation}
Further more, this separation of the image loss from the matching loss open further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.

\subsection{Total Loss}

Our objective for both $D$ and $G$ thus mainly compress two types of terms: \textit{matching aware pair-loss} for matching the overall image content to the text description, and \textit{local adversarial image loss} for rendering the fine-grained details.

In the spirit of variational auto-encoder and the practice of \cite{han2017stackgan}, we also add the  Kullback-Leibler divergence regularization term to the $G$ loss.  %In addition, this term might also play a role in balancing the $c_t$ and generated condition vector $c_t$ by forcing $c$ to have a similar scale to $z$.  In the following sections, we denote $c_t$ as the variational conditional text vector.

\begin{equation}
\label{equ:totalD}
\begin{split}
\mathcal{L}_{d}(D_i, X_i, o_i,\hat{o_i}, t, \hat{t})    = &\mathcal{L}_{pair}(D_i) + \frac{\alpha}{2}~( \\
&\mathcal{L}_{local}(K_i, o_i) + \mathcal{L}_{local}(K_i, \hat{o_i}) )
\end{split}
\end{equation}
\begin{equation}
\label{equ:totalG}
\begin{split}
\mathcal{L}_{g}(G,o,\hat{o}, t)  = &  \mathcal{L}_{pair}(G) + \frac{\alpha}{2}~(\mathcal{L}_{local}(G, o) + \mathcal{L}_{local}(G, \hat{o})) + \\
                  & \beta~D_{KL}(\mathcal{N}(\mu({t}), \Sigma({t}) )|| \mathcal{N}(0, \bm{I})) 
\end{split}
\end{equation}
where $\alpha$ is coefficient used to tune the weight of the local patch loss, $\beta$ is used to tune the weights of the KL-Divergence. 
We omit the additional arguments to both $\mathcal{L}_{pair}(G) $ and $\mathcal{L}_{pair}(D_i) $ for simplicity.
%The loss function of the matching aware discriminator are summarized as:
%\begin{equation}
%\label{matchignloss}
%\begin{split}
%\mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
%&\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
%&   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
%\end{split}
%\end{equation}
%
%\begin{equation}
%\label{matchignloss}
%\begin{split}
%\mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
%&\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
%&   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
%\end{split}
%\end{equation}

 \begin{algorithm}
 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we omit the batch index and summarize the algorithm using SGD for simplicity.}
 	\label{CHalgorithm}
 	\begin{algorithmic}[1]
 		\For{$i \gets 1 \textrm{ to } S$ }
 		\For{$k \gets 1 \textrm{ to } ncritic$}
 		\State Sample two noise batch $z_1, z_2 \sim p(z)$.
 		\State Sample one matching image text pair $\{x, t\}$ and mismatched one $\{x, \hat{t}\}$.
 		\State Generate fake image samples for both $t$ and $\hat{t}$
 		\begin{equation}
 		\begin{split}
	 		& {o} = G(t, z_1) \\
	 		& {\hat{o}} = G(\hat{t}, z_2) 
 		\end{split}
 		\end{equation}
	 		\For{each discriminator $D_i$ }
		 		\State Update $D_i$ by descending the gradient of loss \ref{equ:totalD}:
		 		\begin{equation}
		 		   	\theta_{D_i} = \theta_{D_i}  - \nabla_{\theta_{D_i}} \mathcal{L}_d(D_i, X_i,o_i,\hat{o_i}, t,\hat{t})
		 		\end{equation}
	 		\EndFor
 		\EndFor
 		\State Update the generator by descending it's stochastic gradient of loss \ref{equ:totalG}:
 		\begin{equation}
 		\theta_{G} = \theta_{G}  - \nabla_{\theta_{G}} \mathcal{L}_g(G, o, \hat{o}, t)
 		\end{equation}

@@

\subsection{Implementation Details}
A algorithm that summarizes the training process of our model is given in Algorithm 1.

\begin{equation}
\label{genloss}
\begin{split}
\mathcal{L}_G = & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{sent}( G(z, c_t),  \psi_t) ) ] + \\
& \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
& D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
\end{split}
\end{equation}
where $c_t$ is the variational conditional vector generated from $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$. To make the network differentiable, in practice, we adopted the re-parametric trick\cite{vae}, where $c_t$ is actually computed as $\mu(\psi_t)+\Sigma(\psi_t)\odot \epsilon$, where $\epsilon\in \mathcal{R}^{T}$ is draw from a normal Gaussian distribution.

@@
